From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2017-02-16 2015CompleteDerivation/completeDerivation.tex
Preparing title page for submission

\newif\ifjournal
%\journaltrue
\journalfalse

@@

\title{DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics}
\author{Gabriele Carcassi, Christine A. Aidala, David J. Baker, Lydia Bieri}

\ifjournal
	\institute{G. Carcassi \at
		University of Michigan, Ann Arbor, MI 48109 \\
		\email{carcassi@umich.edu}           %  \\
	}
\else
	\affiliation{University of Michigan, Ann Arbor, MI 48109}
\fi

@@

\begin{abstract}
\textbf{This manuscript is a work in progress.} Ideas are constantly reshaped to find more precise and elegant arguments. It is provided as is to stimulate discussion.  \textbf{Make sure you have the latest version from http://assumptionsofphysics.org}

The aim of this work is to show that particle mechanics, both classical and quantum, Hamiltonian and Lagrangian, can be derived from few simple physical assumptions. Assuming deterministic and reversible time evolution will give us a dynamical system whose set of states form a topological space and whose law of evolution is a self-homeomorphism. Assuming the system is infinitesimally reducible, that giving the state and the dynamics of the whole system is equivalent to giving the state and the dynamics of its infinitesimal parts, will give us a classical Hamiltonian system. Assuming the system is irreducible, that giving the state and the dynamics of the whole system tells us nothing about the state and the dynamics of its substructure, will give us a quantum Hamiltonian system. Assuming kinematic equivalence, that studying trajectories is equivalent to studying state evolution, will give us Lagrangian mechanics and limit the form of the Hamiltonian/Lagrangian to the one with scalar and vector potential forces.
\end{abstract}

@@

Status:
\begin{itemize}
%\item Section \ref{sec:fundamental_model}: Done.

%\item Section \ref{sec:dynamical_systems}: Done.

%\item Section \ref{sec:reducibility}: Done.

%\item Section \ref{sec:relativity}: Done.

\item Section \ref{sec:Lagrangian}: Needs review.

\item Section \ref{sec:quantum_prelude}: Needs review.

\item Section \ref{sec:irreducibility}: Needs review.
\end{itemize}

>>>>

\newif\ifjournal
\journaltrue
%\journalfalse

@@

\title{From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics}
\author{Gabriele Carcassi, Christine A. Aidala, David J. Baker, Lydia Bieri}

\ifjournal
	\institute{G. Carcassi, C. A. Aidala \at
		Physics Department, University of Michigan, Ann Arbor, MI 48109 \\
		\email{carcassi@umich.edu}
		\and
		D. J. Baker \at
		Philosophy Department, University of Michigan, Ann Arbor, MI 48109
		\and
		L. Bieri \at
		Mathematics Department, University of Michigan, Ann Arbor, MI 48109 \\
	}
\else
	\affiliation{University of Michigan, Ann Arbor, MI 48109}
\fi

@@

\begin{abstract}
The aim of this work is to show that particle mechanics, both classical and quantum, Hamiltonian and Lagrangian, can be derived from few simple physical assumptions. Assuming deterministic and reversible time evolution will give us a dynamical system whose set of states form a topological space and whose law of evolution is a self-homeomorphism. Assuming the system is infinitesimally reducible, that giving the state and the dynamics of the whole system is equivalent to giving the state and the dynamics of its infinitesimal parts, will give us a classical Hamiltonian system. Assuming the system is irreducible, that giving the state and the dynamics of the whole system tells us nothing about the state and the dynamics of its substructure, will give us a quantum Hamiltonian system. Assuming kinematic equivalence, that studying trajectories is equivalent to studying state evolution, will give us Lagrangian mechanics and limit the form of the Hamiltonian/Lagrangian to the one with scalar and vector potential forces.
\keywords{Hamiltonian mechanics \and Lagrangian mechanics \and Quantum mechanics \and Fundamental assumptions}
\end{abstract}

@@
